Describing the C-Space of Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-07-30 dit-paper_ieee.tex

	\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.5\textwidth]{python-simulation/plots/nofpdit.png}
	\end{center}
	\caption{Evolution of the existence of FPDIT with the CDF}
	\label{fig:noFPDIT}
	\end{figure}

	We observe that the more we are close to the implicit deadline case, the less systems have FPDIT. This is easily explained by the fact that a lower CDF means more idle instant for each task, and thus more opportunities for DITs to happen. Similarly, as all tasks must be synchronized for a DIT to happen, a higher number of tasks results in a decrease in FPDIT density.

>>>>

	\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.5\textwidth]{python-simulation/plots/nofpdit_3.eps}
	\end{center}
	\caption{Evolution of the existence of FPDIT with the CDF}
	\label{fig:noFPDIT}
	\end{figure}

	We observe that the more we are close to the implicit deadline case ($CDF = 0$), the less systems have FPDIT. This is easily explained by the fact that a lower CDF means more idle instant for each task, and thus more opportunities for DITs to happen. Similarly, as all tasks must be synchronized for a DIT to happen, a higher number of tasks results in a decrease in FPDIT density.
